Interval Probability for Fuzzy Quantum Theories

### 2016-05-15 prob.tex
prob.tex \section{Quantum Probability Spaces} updating... Besides, it seems that git cannot detact swapping text?

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ and $\mathbb{1}$ are a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. 
\item Conversely, every projection~$P$ can be expressed as $\sum_{j}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
\end{itemize}
\end{definition}

Comparing to the classical events, the empty set~$\emptyset$ corresponds
to the empty projection~$\mathbb{0}$, the event of whole sample
space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.

As operators, we can also multiply projections together.

\begin{definition}[Commutativity~\cite{peres1995quantum}]
Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
\end{definition}

% \amr{ 
%   Projections include $\mathbb{0}, \proj{\psi}$ and $P_1 + P_2$ and
%   $P_1 . P_2$ if $P_1$ and $P_2$ commute.
%   When we write an event as $\sum E_i$ we are implicitly assuming they
%   are commutative.
%   Orthogonal implies commutative but not vice-versa
% }
% \yutsung{
%   I checked \\
%   \url{http://math.stackexchange.com/questions/1146893/on-the-sum-of-projection-operators}.\\
%   Actually, they said $P_1 P_2 = P_2 P_1 = 0$, and the last $= 0$ is orthogonal.
% }

@@

>>>>

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ and $\mathbb{1}$ are a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection, where the preposing subscript $\mathscr{O}$
means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
and may be dropped when summands are clearly operators. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. Conversely, every projection~$P$ can be expressed as $\sum_{j}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
\end{itemize}
\end{definition}

Based on the set of events, we can define the quantum probability
space.

@@

Comparing to the classical probability space, the empty set~$\emptyset$
corresponds to the empty projection~$\mathbb{0}$ and the event of
whole sample space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
In contrast, the union~$\cup$ of any two events always gives an
event classically, the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
of two projections may not be a projection. As the result, the equation
$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
however, $\mu\left(E_{1}\tensor*[_{\mathscr{O}}]{+}{}E_{2}\right)=\mu(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(E_{2})$
is always true whenever the left-handed side is defined. Whether equation
is defined also effects the further properties of quantum probability
space.

\begin{definition}{[}Orthogonal Complement; Commutativity~\cite{peres1995quantum}{]} 
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{O}]{-}{}P$
is also a projection operator.
\end{itemize}
Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
\end{definition}
